---
title: "`(prep -> plot -> print)`: Technique for Reproducible Graphing"
date: "Date: `r Sys.Date()`"
author: "Andriy Koval"
output: 
  html_document: 
    keep_md: no
    toc: yes
    toc_float: 
      collapsed: true
      smooth_scroll: true
    highlight: haddock
    theme: simplex
---

# overview

This document captures applications of  `(prep + plot + print) + place` technique using the data from VADA 2019 Summer School Data Challenge. See  [github.com/andkov/vada-2019-summer-school](https://github.com/andkov/vada-2019-summer-school) repository for reproducible scripts.

A fully reproducible example of the same technique using the publically available data from the Canadian Chronic Disease Surveillance System (CCDSS) is featured at [`github.com/dss-ialh/graph-making-scenarios]`(https://github.com/dss-ialh/graph-making-scenarios/blob/master/README.md)

The technique for reproducible graphing demonstrated here procedes in the following sequence of phases:

- PHASE 0 - explore the data
- PHASE 1 - build the plot
- PHASE 2 - build the `plot` function
- PHASE 3 - split into `prep` and `plot` functions
- PHASE 4 - add the `print` function
- PHASE 5 - serialize graph production
- PHASE 6 - how to `place` graphs onto the canvas


<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
library(knitr)
opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
# cat("Working directory: ", getwd())
report_render_start_time <- Sys.time()
opts_chunk$set(
  results      = 'show', 
  comment      = NA, 
  tidy         = FALSE,
  # dpi        = 400,
  # out.width  = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.
  fig.width    = 7, 
  fig.height   = 4, 
  fig.path     = 'figure-png/'
)

echo_chunks    <- TRUE #Toggle for debugging.
message_chunks <- FALSE #Toggle for debugging.
warning_chunks <- FALSE
options(width=100) #So the output is 25% wider than the default.
read_chunk("./analysis/prep-plot-print/prep-plot-print-00-applications.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

# set the scene

## load packages
<!-- Load packages, or at least verify they're available on the local machine.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echo_chunks,warning=warning_chunks, message=message_chunks}
```
## load sources
<!-- Load 'sourced' R files.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echo_chunks,warning=warning_chunks, message=message_chunks}
```
## declare globals
<!-- Load any global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echo_chunks, results='show', warning=warning_chunks,message=message_chunks}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. -->
```{r rmd-specific, echo=echo_chunks, warning=warning_chunks,message=message_chunks}
# Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
#   It should be rare (and used cautiously), but sometimes it makes sense to include code in Rmd 
#   that doesn't live in the codebehind R file.
```
## load data
<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show',warning=warning_chunks, message=message_chunks}
```

## tweak data
<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show',warning=warning_chunks, message=message_chunks}
```

# examples

## example-1 
```{r example-1, echo=echo_chunks, results='asis',warning=warning_chunks, message=message_chunks,fig.width=11, fig.height=7,out.width="960px"}
```

## example-2
```{r example-2, echo=echo_chunks, results='asis',warning=warning_chunks, message=message_chunks,fig.width=11, fig.height=7,out.width="960px"}
```

## example-3
```{r example-3, echo=echo_chunks, results='asis',warning=warning_chunks, message=message_chunks,fig.width=11, fig.height=7,out.width="960px"}
```



session information
===========================================================================

For the sake of documentation and reproducibility, the current report was rendered in the following environment.  Click the line below to expand.

<details>
  <summary>Environment <span class="glyphicon glyphicon-plus-sign"></span></summary>
```{r session-info, echo=FALSE}
if( requireNamespace("devtools", quietly = TRUE) ) {
  devtools::session_info()
} else {
  sessionInfo()
} 
```
</details>

```{r session-duration, echo=FALSE}
report_render_duration_in_seconds <- round(as.numeric(difftime(Sys.time(), report_render_start_time, units="secs")))
```

Report rendered by `r Sys.info()["user"]` at `r strftime(Sys.time(), "%Y-%m-%d, %H:%M %z")` in `r report_render_duration_in_seconds` seconds.